---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# bivnegbincp
`bivnegbincp` provides Bayesian multiple change-point detection for bivariate negative binomial count data.

## Installation

You can install the development version of bivnegbincp like so:

```{r}
# install.packages("remotes")
# remotes::install_github("asinha639/bivnegbincp")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bivnegbincp)

set.seed(123)

x1 <- c(
  rnbinom(50, size = 10, mu = 5),
  rnbinom(25, size = 10, mu = 12),
  rnbinom(25, size = 10, mu = 20)
)

x2 <- c(
  rnbinom(50, size = 8, mu = 4),
  rnbinom(25, size = 8, mu = 10),
  rnbinom(25, size = 8, mu = 18)
)

res <- bivnegbin_singlecp(
  x1 = x1,
  x2 = x2
)

str(res, max.level = 1)
```


## Output
The function returns model output and detected change-point information for the two count series.


